\section*{Budget Justification}

\subsection*{A. Senior Personnel}

\noindent{\bf A1.} Person One, Title and Affiliation, will serve as PI on this project and oversee blah blah. We request 1 month of summer salary per year for Dr. Person One, which is based on a rate of \$10,000/month and includes a 2\% annual escalation:
\newline
\begin{table}[h]
\begin{tabular}[c]{cccc}
Year 1: \$10,000 & Year 2: \$10,200 & Year 3: \$10,404 & Total: \textbf{\$30,604}
\end{tabular}
\end{table}
\newline
\newline
\noindent{\bf A2.} Person Two, Title and Affiliation, will serve as Co-PI on this project and will do nothing. We request 1 month of summer salary per year for Dr. Person Two, which is based on a rate of \$10,000/month and includes a 2\% annual escalation:
\newline
\begin{table}[h]
\begin{tabular}[c]{cccc}
Year 1: \$10,000 & Year 2: \$10,200 & Year 3: \$10,404 & Total: \textbf{\$30,604}
\end{tabular}
\end{table}

\subsection*{B. Other Personnel}
\noindent{\bf B3.} We request salary support for one PhD student, which is based on a rate of \$25,000/year and a 2\% annual escalation. The student will bring Persons One and Two coffee upon request.
\newline
\begin{table}[h]
\begin{tabular}[c]{cccc}
Year 1: \$25,000 & Year 2: \$25,500 & Year 3: \$26,010 & Total: \textbf{\$76,510}
\end{tabular}
\end{table}

\noindent{\bf B4.} We request salary support for two part-time undergraduate students, which is based on a rate of \$10/hour for 10 hours/week during the academic year (360 hours) and 40 hours/week during the summer (560 hours). The students will tweet nice things about Persons One and Two.
\newline
\begin{table}[H]
\begin{tabular}[c]{cccc}
Year 1: \$18,400 & Year 2: \$18,400 & Year 3: \$9,200 & Total: \textbf{\$46,000}
\end{tabular}
\end{table}

\subsection*{C. Fringe Benefits}
Fringe benefits at the University of Whatevs are calculated at a rate of 35\% for faculty and 8\% for students. Following these guidelines, we request the following amounts for benefits.
\newline
\begin{table}[H]
\begin{tabular}[c]{r r r r | r}
                & Year 1     & Year 2     & Year 3     & Total\\
 Person One     & \$3,500    & \$3,570    & \$3,641    & \$10,711\\
 Person Two     & \$3,500    & \$3,570    & \$3,641    & \$10,711\\
 PhD Student    & \$2,000    & \$2,040    & \$2,081    & \$6,121\\
 Ugrad Student  & \$1,472    & \$1,472    & \$736      & \$3,680\\
 \hline
 Total          & \$10,472   & \$10,652   & \$10,099   & \textbf{\$31,223} \\
\end{tabular}
\end{table}

\subsection*{D. Equipment}
We will purchase a powerful workstation to play on Facebook. We will purchase 200TB of archive storage from the University of Whatevs to enable the dissemination of memes and gifs.
\newline
\begin{table}[H]
\begin{tabular}[c]{r | r}
 & Total\\
Workstation     & \$10,000\\
200 TB Storage  & \$32,000\\
\hline
Total           & \textbf{\$42,000}
\end{tabular}
\end{table}

\subsection*{E. Travel}
PI Person One, PI Person Two, and the PhD student plan to attend vacations in small-town America. We request the following travel funds to cover airfare, per diem, and booze.
\newline
\begin{table}[H]
\begin{tabular}[c]{cccc}
Year 1: \$4,400  & Year 2: \$4,400    & Year 3: \$4,400    & Total: \textbf{\$13,200}
\end{tabular}
\end{table}

\subsection*{E. Participant Support Costs}
There are no participant support costs associated with this project.

\subsection*{G. Other Direct Costs}
We plan to publish the results of our study in Years 2 and 3. We project that results will be verifiable and provide data that will produce information which will be disseminated through conferences where people waste time hearing themselves talk and publication in obscure journals that no one actually reads. A desktop computer will be used to conduct this work and to read TMZ when we are bored. Additionally, we anticipate the need for external local disk storage, software licenses, and repair fees for existing workstations. We also are requesting funds in each project year to support miscellaneous costs associated with the outreach activities, such as Snapchat filters.  These costs may include: basic supplies (notebooks, clipboards, etc.) and subscriptions to HBO Now and Showtime Anytime.
\newline
\begin{table}[H]
\begin{tabular}[c]{r r r r | r}
 & Year 1 & Year 2 & Year 3 & Total\\
Publication Charges     & \$0        & \$3,000    & \$3,000    & \$6,000\\
Desktop Computer        & \$2,750    & \$0        & \$0        & \$2,750\\
Technology Supplies     & \$1,000    & \$1,000    &\$1,000     & \$3,000\\
Outreach Supplies       & \$2,000    & \$2,000    &\$2,000     & \$6,000\\
\hline
Total                   & \$5,750   & \$6,000   & \$6,000 & \textbf{\$17,750}
\end{tabular}
\end{table}

\subsection*{H. Indirect Costs}

\noindent The modified total direct cost for each year was multiplied by the corresponding negotiated overhead rate. The indirect costs are summarized below.
\newline
\newline
\begin{table}[H]
\begin{tabular}[c]{r r r | r}
        & Direct Costs  & Rate      & Total\\
Year 1  & \$84,022      & 51.0\%    & \$42,851\\
Year 2  & \$85,352      & 51.5\%    & \$43,956\\ 
Year 3  & \$76,517      & 52.5\%    & \$40,171\\
\hline
        &               & Total     & \textbf{\$126,978}
\end{tabular}
\end{table}