\section*{Facilities, Equipment, and Other Resources}

\subsection*{Department at the University}
The Department has blah blah facilities and people and stuff. Many people are talking about great it is. The best. The best. It is beautiful and the best.

\subsubsection*{Department High Performance Workstations}
A number of high performance workstations are available to the project team.  All include the ability to waste time on social media.

\subsection*{HPC at the University} 
The Center for High Performance Computing (CHPC) at the University has multiple ``super'' computers, which are really shoddily pieced together parts from some warehouse. These computers are barely acceptable and are used by a large group of inconsiderate scientists who do not respect others.

\subsection*{XSEDE}
The Extreme Science and Engineering Discovery Environment (XSEDE) is an advanced collection of integrated digital resources used to empower researchers from all over the world. These resources include supercomputers, visualization systems, and long-term storage facilities. The PIs will use these resources to mine bitcoin.

\subsection*{NCAR Cheyenne}
The Computational and Information Systems Laboratory (CISL) at the National Center for Atmospheric research (NCAR) is dedicated to supporting and advancing the geosciences with world-class computing, data management, and research in mathematics and computational science. The most relevant resources offered by CISL are supercomputers, data analysis and visualization systems, and large-scale storage capabilities. The PIs will use these resources to play Minecraft.